Simulation with algorithm 2

### 2021-09-13 supplementary/algorithm3/real-data/handpick-18.Rmd
add structure to methodology

# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==1) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
# 
# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==2) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
```

@@

>>>>

# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==1) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
# 
# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==2) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))

@@

```{r scaled-data}

data_pick_scaled <- data_pick %>%
    group_by(customer_id) %>%
    dplyr::mutate(kwh_scaled = stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x) %>%
    ungroup()

quantile_prob_val = c(0.25, 0.5, 0.75)

#sm_hod_scaled <- gravitas::create_gran(data_pick_scaled, "hour_day")

sm_hod_all <- data_pick %>% 
bind_cols(data_pick_scaled %>% as_tibble() %>% select(kwh_scaled)) %>% 
  rename("kwh" = "general_supply_kwh") %>% 
gravitas::create_gran("hour_day") %>% 
  pivot_longer(c(5, 11), names_to = "kwh_type", values_to = "kwh_value")

sm_hod_all %>%
filter(design ==1) %>%
ggplot(aes(x = kwh_value, y = hour_day, fill = kwh_type)) +
ggridges::geom_density_ridges(alpha = 0.5) +
facet_wrap(~customer_id, scales = "free_x") +
  stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.5) +
    coord_flip() +
  theme(legend.position = "bottom")

sm_hod_all %>%
filter(customer_id %in% c(8181071)) %>%
ggplot(aes(x = kwh_value, y = hour_day), fill = "blue") +
ggridges::geom_density_ridges(alpha = 0.5) +
facet_grid(customer_id~kwh_type, scales = "free_x") +
  stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.5, color = "blue") +
    #coord_flip() +
  theme(legend.position = "bottom")

sm_hod_all %>%
filter(customer_id %in% c(11013154)) %>%
ggplot(aes(x = kwh_value, y = hour_day), fill = "blue") +
ggridges::geom_density_ridges(alpha = 0.5) +
facet_grid(customer_id~kwh_type, scales = "free_x") +
  stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.5, color = "blue") +
    #coord_flip() +
  theme(legend.position = "bottom")

quantile_q2 <-  function(x){
  y = quantile(x, probs = c(0.5))
  #c(y[1], y[2]) %>% as_tibble() %>% bind_cols(names(y)) %>% set_names(c("quant_value", "quantile"))
}

quantile_q1 <-  function(x){
  y = quantile(x, probs = c(0.25))
  #c(y[1], y[2]) %>% as_tibble() %>% bind_cols(names(y)) %>% set_names(c("quant_value", "quantile"))
}

quantile_q3 <-  function(x){
  y = quantile(x, probs = c(0.75))
  #c(y[1], y[2]) %>% as_tibble() %>% bind_cols(names(y)) %>% set_names(c("quant_value", "quantile"))
}

# sm_hod_all %>%
# filter(customer_id %in% c(8955520)) %>%
# ggplot(aes(x = kwh_value, y = hour_day), fill = "blue") +
# ggridges::geom_density_ridges(alpha = 0.5) +
# facet_grid(customer_id~kwh_type, scales = "free_x") +
#   ggridges::stat_density_ridges(quantile_lines = TRUE, quantiles = 0.9) + stat_summary(
#     fun = quantile_q2,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "blue") +
#     #coord_flip() +
#   theme(legend.position = "bottom")

#one_peak

sm_hod_all %>%
filter(customer_id %in% c(8198401)) %>%
ggplot(aes(x = kwh_value, y = hour_day), fill = "#999999") +
ggridges::geom_density_ridges(alpha = 0.7) +
facet_wrap(~kwh_type, scales = "free_y", ncol = 1) +
  stat_summary(
    fun = quantile_q2,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "blue") +
    coord_flip() +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q1,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
  theme(legend.position = "bottom") +
   stat_summary(
    fun = quantile_q3,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
    #coord_flip() +
  theme(legend.position = "bottom") +
  theme_bw()

# two peaks
sm_hod_all %>%
filter(customer_id %in% c(10469265)) %>%
ggplot(aes(x = kwh_value, y = hour_day), fill = "#999999") +
ggridges::geom_density_ridges(alpha = 0.7) +
facet_wrap(~kwh_type, scales = "free_y", ncol = 1) +
  stat_summary(
    fun = quantile_q2,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "blue") +
    coord_flip() +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q1,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
  theme(legend.position = "bottom") +
   stat_summary(
    fun = quantile_q3,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
    #coord_flip() +
  theme(legend.position = "bottom") +
  theme_bw()

# Three peaks

sm_hod_all %>%
filter(customer_id %in% c(10046512)) %>%
ggplot(aes(x = kwh_value, y = hour_day), fill = "#999999") +
ggridges::geom_density_ridges(alpha = 0.7) +
facet_wrap(~kwh_type, scales = "free_y", ncol = 1) +
  stat_summary(
    fun = quantile_q2,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "blue") +
    coord_flip() +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q1,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
  theme(legend.position = "bottom") +
   stat_summary(
    fun = quantile_q3,
    geom = 'line',
    aes(group = 1), size = 0.7, color = "#D55E00") +
    #coord_flip() +
  theme(legend.position = "bottom") +
  theme_bw()

# sm_hod_all %>%
# filter(customer_id %in% c(8198401)) %>%
# ggplot(aes(x = kwh_value, y = hour_day), fill = "#999999") +
# ggridges::geom_density_ridges() +
# facet_grid(customer_id~kwh_type, scales = "free_x") +
#   stat_summary(
#     fun = quantile_q2,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "blue") +
#     #coord_flip() +
#   theme(legend.position = "bottom") +
#   stat_summary(
#     fun = quantile_q1,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "#D55E00") +
#   theme(legend.position = "bottom") +
#    stat_summary(
#     fun = quantile_q3,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "#D55E00") +
#     #coord_flip() +
#   theme(legend.position = "bottom") +
#   theme_bw()

# sm_hod_all %>%
# filter(customer_id %in% c(10469265)) %>%
# ggplot(aes(x = kwh_value, y = hour_day), fill = "#999999") +
# ggridges::geom_density_ridges() +
# facet_grid(customer_id~kwh_type, scales = "free_x") +
#   stat_summary(
#     fun = quantile_q2,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "blue") +
#     #coord_flip() +
#   theme(legend.position = "bottom") +
#   stat_summary(
#     fun = quantile_q1,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "#D55E00") +
#   theme(legend.position = "bottom") +
#    stat_summary(
#     fun = quantile_q3,
#     geom = 'line',
#     aes(group = 1), size = 0.5, color = "#D55E00") +
#     #coord_flip() +
#   theme(legend.position = "bottom") +
#   theme_bw()

p1 <- sm_hod %>% 
filter(design ==1) %>% 
ggplot(aes(x = general_supply_kwh, y = hour_day)) +
ggridges::geom_density_ridges(alpha = 0.05) +
facet_wrap(~customer_id, nrow = 6) + 
  stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.5) +
    coord_flip()

p2 <- gravitas::create_gran(data_pick_scaled, "hour_day") %>% 
filter(design ==1) %>% 
ggplot(aes(x = kwh_scaled, y = hour_day)) +
ggridges::geom_density_ridges(alpha = 0.05, fill = "grey") +
facet_wrap(~customer_id, ncol = 2, scales = "free_x") + 
  stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.5) +
    coord_flip() + theme_bw()

# %>% 
#   left_join(categories_ref_cat) %>% 
#   rename("category" = "value") %>% 
#   select(-categories_serial_id) %>% 
#   mutate(category = as.numeric(category))

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")

### 2021-09-13 supplementary/algorithm3/simulation-data/diffmeans-threegran-5designs.Rmd
add structure to methodology

```{r}
seed_len = seq(12345, 12348, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_design_2 <- generate_design(t = 599, mu = c(0, 2))
data_design_3 <- generate_design(t = 599, mu = c(0, 2, 4))
data_design_4 <- generate_design(t = 599, mu = c(0, 2, 4, 6))
data_design_1 <- generate_design(t = 599, mu = 0)
data_design_5 <- generate_design(t = 599, mu = c(0, 2, 4, 6, 8, 10))
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4,data_design_5, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))
}) %>% bind_rows(.id = "seed_id")

@@

<!-- Cross-check -->
<!-- data = bind_data_iter %>% filter(design == "design-2", seed_id == 5) -->
<!-- p2 <- ggplot(data, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- p3 <- ggplot(data, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- p4 <- ggplot(data, aes(x = as.factor(g3), y = value)) + geom_boxplot() + -->
<!-- xlab("g3") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- (p2 + p3 + p4) -->

<!-- ```{r} -->
<!-- p2 <- ggplot(data, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw() -->
<!-- p3 <- ggplot(data, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw() -->
<!-- p4 <- ggplot(data, aes(x = as.factor(g3), y = value)) + geom_boxplot() + -->
<!-- xlab("g3") + theme_bw()  -->
<!-- (p2 + p3 + p4) -->
<!-- ``` -->

```{r}
harmony_tbl <- tibble(facet_variable = NA, x_variable = c("g1", "g2", "g3"),
                      x_levels = c(2, 3, 4), facet_levels = NA)
```

```{r wpd-table}
data <- bind_data_iter %>% mutate(data_id = paste(design, seed_id, sep = "-"))
bind_data_iter <- tsibble::as_tsibble(data, index = t, key = "data_id")

data_wpd <- map(seq_len(length(unique(bind_data_iter$data_id))),
    function(y){
      z = unique(bind_data_iter$data_id)
      data_sub <- bind_data_iter %>% filter(data_id==z[y])
        elec_select_harmony = hakear::select_harmonies(data_sub,
                               harmony_tbl = harmony_tbl,
                               response = value,
                               nperm = 200
  ) %>% mutate(data_id = unique(data_sub$data_id)) %>% unnest()
    }) %>% bind_rows()

write_csv(data_wpd, "data_wpd.rds")
```

# Table of wpd across designs and wpd

```{r data-wide}

data_wide <- data_wpd %>% select(x_variable, wpd, data_id) %>% 
  pivot_wider(names_from = x_variable, values_from = wpd)
data_wide %>% kable()

ggpairs_nocolor <- ggpairs(data_wide, columns = 2:4)

rownames(data_wide) = data_wide$data_id

hc = stats::hclust(dist(data_wide[-1], method = "manhattan"),method="complete")

library(fpc)
koptimal = fpc::nselectboot(dist(data_wide[-1], method="manhattan"),
                        B = 500,
                        method = "complete",
                        clustermethod = disthclustCBI, 
                        classification = "averagedist",
                        krange = 2:8)

koptimal = koptimal$kopt
```

# Clustering of designs

```{r}
  groups <- cutree(hc, k=5) %>% as_tibble() %>% 
mutate(data_id = data_wide$data_id) %>% rename("group" = "value")

  groups %>% kable()

data_wide_group <- data_wide %>% left_join(groups)  %>% 
  mutate(group_id = as.factor(group))

parcoord <- GGally::ggparcoord(data_wide_group,
                   columns = 2:ncol(data_wide),
                   groupColumn = "group_id",
                   showPoints = TRUE, 
                   title = "(c)",
                   alphaLines = 0.8,
                   scale = "globalminmax", 
                   order = "anyClass"
) + ggplot2::theme_bw() +
  scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.y = ggplot2::element_text(angle = 0)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")
parcoord
ggpairs_nocolor
  # ggpairs_color <- ggscatmat(data_wide, columns=2:4, color = "group") +
  # scale_colour_brewer(palette="Set2")
```

# With optimal number of clusters

Design 2 and 4 form a part of the same cluster with the optimal number of clusters chosen as 4. Design 2 and 4 are similar in the sense that both of them changes across categories for g1 and g3, and remains constant for g2.

```{r}
  groups <- cutree(hc, k=koptimal) %>% as_tibble() %>% 
mutate(data_id = data_wide$data_id) %>% rename("group" = "value")

  groups %>% kable()

data_wide_group <- data_wide %>% left_join(groups)  %>% 
  mutate(group_id = as.factor(group))

parcoord <- GGally::ggparcoord(data_wide_group,
                   columns = 2:ncol(data_wide),
                   groupColumn = "group_id",
                   showPoints = TRUE, 
                   title = "(c)",
                   alphaLines = 0.8,
                   scale = "globalminmax", 
                   order = "anyClass"
) + ggplot2::theme_bw() +
  scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.y = ggplot2::element_text(angle = 0)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")
parcoord
ggpairs_nocolor
  # ggpairs_color <- ggscatmat(data_wide, columns=2:4, color = "group") +
  # scale_colour_brewer(palette="Set2")
```

# PCA based clustering

```{r}
pc <- prcomp(data_wide_group[c(2, 3, 4)], center = F, scale = F)

# First two principal componentsafc
comp <- data.frame(pc$x[,1:2])

#plot(comp, pch=16, col=rgb(0,0,0,0.5))

hc = stats::hclust(dist(comp))
groups <- cutree(hc, k=koptimal) %>% as_tibble() %>% bind_cols(comp) %>% 
  mutate(value = as.character(value))
library(RColorBrewer)
library(scales)
groups %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = value)) +
  scale_color_brewer(palette = "Dark2") + theme_bw()
```

>>>>

```{r}
seed_len = seq(12345, 12348, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_design_2 <- generate_design(t = 599, mu = c(0, 2))
data_design_3 <- generate_design(t = 599, mu = c(0, 2, 4))
data_design_4 <- generate_design(t = 599, mu = c(0, 2, 4, 6))
data_design_1 <- generate_design(t = 599, mu = 0)
data_design_5 <- generate_design(t = 599, mu = c(0, 2, 4, 6, 8, 10))
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4,data_design_5, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))
}) %>% bind_rows(.id = "seed_id")
```

```{r}

quantile_prob_val = seq(0.1,0.9,0.1)
bind_data_iter <- bind_data_iter %>% mutate(
  customer_id  = paste0(design,"-s-", seed_id)) %>%
   as_tsibble(key=customer_id,index=t)

library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g1", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val))%>% rename("dist_g1" = "dist")

v3 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g2", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_g2" = "dist")

v4 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g3", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_g3" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  left_join(v4) %>% 
  mutate(dist = dist_g1 + dist_g2 +dist_g3) %>% 
    pivot_wider(-c(3, 4, 5), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")

@@

```{r groups}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=5), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
groups %>% filter(group==1)
groups %>% filter(group==2)
groups %>% filter(group==3)
groups %>% filter(group==4)
groups %>% filter(group==5)
#groups %>% filter(group==4)
```
